Democratizing MPC

### 2017-10-11 OaklandSubmission/intro.tex
1.1

Finally, our framework \tool can serve as a meaningful baseline for future works on hand-crafted SMC protocols for specific functionalities such as \textsc{MiniONN} \cite{minionn}. 
Prior to our work, garbled circuit based two-party computation is cited as the most practical approach and used as the baseline comparison of performance. But, it has been observed multiple times this approach does not scale on realistic examples.

>>>>

Finally, our framework \tool can serve as a meaningful baseline for future works on hand-crafted SMC protocols for specific functionalities such as \textsc{MiniONN} \cite{minionn}. 
Prior to our work, garbled circuit based two-party computation is cited as the most practical approach and used as the baseline for comparison of performance. But, it has been observed multiple times this approach does not even scale on realistic examples.
